---
title: "index.Rmd"
author: "Daniel Choi & Renae Wong"
date: "5/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(kableExtra)

vaers2021df <- read.csv("data/2021VAERSDATA.csv", stringsAsFactors = FALSE)
```

## Introduction

The COVID-19 Pandemic has changed many things. Due to the pandemic, many people
have died, lost their jobs, and have been restricted from communicating and
interacting in-person. We as a group wanted to explore what the specific
aftermaths were of these issues. By analyzing and researching in depth of the relations
of adversity the majority of people faced, we came to the conclusion of using this [dataset](https://www.kaggle.com/ayushggarg/covid19-vaccine-adverse-reactions?fbclid=IwAR2aQKWsmC7TMTk3TJ-hVX0Hnpl-ajPINOqKOU5wcDmxsgx8EeQXzIQ8smw).

## Summary
```{r, echo = FALSE, results=FALSE, warning = FALSE}
# get summary information from scripts/summary_information.R
source("scripts/summary_information.R")
summary_info <- summary_info(vaers2021df)
```

In this data set, we hope to explore the different ways people were affected
by COVID-19, by their location, gender, age, and number of days until they experienced
adverse effects due to the COVID-19 or the COVID-19 vaccine. From this data set
we were able to discover that there were `r summary_info$male_num` males and
`r summary_info$female_num` females, with the average age in the data set
being `r summary_info$avg_age`. In this dataset, there were `r summary_info$features`
features and `r summary_info$observations` participants.

## Table

This table below shows us the gender of participants in each state, and the 
average age of each participant. We included this table as it reveals the sex, location, and the average age, which allows us to answer our question of research "Which age groups and genders were most impacted by COVID-19, and in which locations were they located in?" Through this table, we were able to gain further insight towards how our participants were impacted due to the
COVID pandemic. I used the summarize function to find the sum of the male, female, and unknown
genders. I also used the summarize function to find the average of each age. This table is
ordered in the highest to lowest average age recorded.

```{r, echo=FALSE, warning = FALSE}
# get table from scripts/Aggregate Table Script.R
source("scripts/Aggregate Table Script.R")
kable(aggregate_info(vaers2021df)) %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  column_spec(1, bold = TRUE, italic = TRUE) %>%
  row_spec(1, bold = TRUE, background = "black", color = "white",
           italic = FALSE)
```


$$\\[.1in]$$

# Charts

$$\\[.1in]$$

## Chart 1
```{r, echo = FALSE, warning = FALSE}
## Chart 1
# load first chart from script/chart_1.R
source("scripts/chart_1.R")
chart_1 <- chart_1(vaers2021df)
chart_1
```

We used a scatter plot to measure the adverse effects of the COVID-19 
for each state and separated the data to consider the gender of the participants
and the age, where the red signifies the female, green signifies the male, and
blue signifies the unknown gender. We included this chart in an attempt to seek
the difference age, gender, or location would seem to have on people of the
respective pool of research. This information/the chart itself reveals a scatter plot
where each dot represents a single participant. Through this, we were able to
answer our question of "How has COVID-19 impacted the people of different genders,
location, and age."


$$\\[.1in]$$

## Chart 2
```{r, echo=FALSE, warning = FALSE}
## Chart 2
# load first chart from script/chart_1.R
source("scripts/chart_2.R")
chart_2 <- chart_2(vaers2021df)
chart_2
```

For Chart 2, we attempted to give the visual distribution of gender alone. We
wanted to create a chart that would allow us and the users of this information
to be given a clear and concise visual that would allow them to understand the
overall distribution of males, females, and unknown genders that were recorded into
the data set. We seeked to express our question of "What genders were included in
this data set, and what was the general distribution of each gender?" The chart
itself is a pie chart which reveals the distribution of each gender.

$$\\[.1in]$$

## Chart 3
```{r, echo=FALSE, warning = FALSE}
## Chart 3
# load first chart from script/chart_1.R
source("scripts/chart_3.R")
chart_3 <- chart_3(vaers2021df)
chart_3
```

For our last chart, we wanted to compare the relationship of age and how long it
took for the side effects of the COVID-19 Vaccine to occur and how it differed
between the ages of each participant. We decided that a bar graph which would show
the distribution of each age category horizontally, along with the number of hours
labeled vertically, would adequately display and answer our question of "How has the
COVID-19 Vaccine affected the different age groups?" This information is shown below
through a bar graph.

$$\\[.1in]$$
